A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-08-26 demystify.tex
updates

    % Year
    \draw[ultra thick,gray]
    ($(current page.center)+(5,2)$) -- ++(0,-3cm) 
    node[
    midway,
    left=0.25cm,
    text width=5cm,
    align=right,
    black!75
    ]
    {
    {\fontsize{25}{30} \selectfont \bf Computer\\[8pt] Science}
    } 
    node[
    midway,
    right=0.25cm,
    text width=6cm,
    align=left,
    ForestGreen]
    {
    {\fontsize{48}{50} \selectfont PhD}
    };

    % Title
    \node[align=center] at ($(current page.center)+(0,-5)$) 
    {
    {\fontsize{24}{24} \selectfont {{Demystifying the Computer Science}}} \\[0.15in]
    {\fontsize{24}{24} \selectfont {{PhD Admission in the US}}} \\[0.2in]    
    {\fontsize{18}{18} \selectfont {{A Handbook for International Students}}} \\[0.5in]

>>>>

    % Year
    \draw[ultra thick,gray]
    ($(current page.center)+(5,3.5)$) -- ++(0,-3cm)
    node[
    midway,
    left=0.25cm,
    text width=5cm,
    align=right,
    black!75
    ]
    {
    {\fontsize{25}{30} \selectfont \bf Computer\\[8pt] Science}
    } 
    node[
    midway,
    right=0.25cm,
    text width=6cm,
    align=left,
    ForestGreen]
    {
    {\fontsize{48}{50} \selectfont PhD}
    };

    % Title
    \node[align=center] at ($(current page.center)+(0,-7)$)
    {
    {\fontsize{24}{24} \selectfont {{Demystifying the Computer Science}}} \\[0.15in]
    {\fontsize{24}{24} \selectfont {{PhD Admission in the US}}} \\[0.2in]    
    {\fontsize{18}{18} \selectfont {{A Handbook for International Students}}} \\[1.in]

### 2024-08-26 faculty.tex
updates

This section focuses on research publication, which is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues.
%P\&T members or letter writers (obviously) are familiar with top places in your field, and they will definitely look for those in your profile.
Work that won awards, e.g., best paper awards, can help a lot in P\&T. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

@@

\paragraph{Artifact Evaluation} This is probably more well-known in SE conferences, and is intended to promote the reproducibility of research results. However, I never liked it because it's a lot of work and many of my experiments require heavy computation that the reviewers do not have.  I also don't think it's very useful as I have always make my code, benchmarks, and results open source (through Github). I found it strange that many SE conference have recently required this as part of the submission process. It makes the submission process much more complicated and much more time-consuming.

@@

While many faculty do not value short papers, I find that they are are very useful for writing grant proposals. They show that you have a new idea and good preliminary results that are worth pursuing further. Sometimes a full paper is not as good because the research is relatively complete with strong results, which bring the concern that you already did all the cool work and the proposal is minor and not exciting.

>>>>

This section focuses on research publication, which is a major component of P\&T and of course in getting your name out there. P\&T evaluation requires no specific conferences/journals or numbers of papers, but typically you will want to have a good number of papers in top venues.
Work that won awards, e.g., best paper awards, can help a lot in P\&T. Papers with very high citations also help.  Research areas that you started and are now popular also count.  Finally, new research directions that can help get grants are also good.

@@

@@

While many faculty do not value short papers, I find that they are are very useful for writing grant proposals. They show that you have a new idea and good preliminary results that are worth pursuing further. Sometimes a full paper is not as good because the research is relatively complete with strong results, which bring the concern that you already did all the cool work and the proposal is minor and not exciting.
I have used results from short papers in many of my grants, e.g., NIER (New Idea and Emerging Results) papers for my NSF CAREER and Tool Demo and SEIP (SE in Practice) paper for my Facebook gift.

\paragraph{Artifact Evaluation (AE)} AE is is probably more well-known in SE conferences, but it allows authors of accepted papers to submit their tools to be evaluated by reviewers. The intention is to show that your research is reproducible. However, I never liked it because it's a lot of work and many of my experiments require heavy computation that the reviewers do not have. In many cases reviewers are students and have no technical expertise how to run things (even though it is already in Docker) or insists on using their own environment (e.g., Mac) while the developed tool is explicitly for Linux.
Finally, I also don't think it's very useful as I have always make my code, benchmarks, and results open source (through Github). I found it strange that many SE conference have recently required this as part of the submission process. It makes the submission process much more complicated and time-consuming.
